---
title: "Codebook"
author: "AnHiVa"
date: "27/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pander)
```

# Variables

The tidy data set contains 180 obs and 68 variables, its saved in ['text'](https://github.com/AnHiVa/AnHiVa--Getting-and-Cleaning-Data-Course-Project/blob/master/TIDY_HumanActivity.txt) and ['csv'](https://github.com/AnHiVa/AnHiVa--Getting-and-Cleaning-Data-Course-Project/blob/master/TIDY_HumanActivity.csv) file formats. 

### Variable list

- subject: ID of the subject tested (1:30) 
- activity: Activity name (WALKING, SITTING, LAYING...)

The rest of the variables are a combination of features:

- Domain: Time or Frequency
- Instrument: Accelerometer or Gyroscope
- Acceleration: Body or Gravity
- Magnitude
- Jerk
- Axis: X, Y or Z direction
- Statistical measurement: Mean or Standard Deviation (STD)


```{r variable names, echo=FALSE}
Summarized_Data <- read_csv("TIDY_HumanActivity.csv", col_types = cols())
Variables <- as_tibble(names(Summarized_Data))
Variables <- rename(Variables, Variables = value)
pander(Variables)
```

# Summaries calculated

A 10 x 6 example is shown below

```{r pressure, echo=FALSE}
head(Summarized_Data, n = c(10,6))
```
